Index measures for oak decline severity using phenotypic descriptors

### 2019-12-11 manuscript/manuscript.Rmd
added discussion point

- Accessability of collecting descriptors
- Suitability of collected phenotypic descriptors for describing decline status
- Concession of model interpretability to predictive capability by using a machine learning approach
- Trends of key phenotypic descriptors withing the PDI and DAI measures
- Sensitivity provided for integration with large scale omics analyses as well as long term monitoring for forest condition
- Index thresholds for category definitions (healthy, declining, severe decline etc.)
- Semi-supervised can be used if unsupervised model is unable to pull out decline severity scale
- Scalability of method for wider application
- When viewed in the 2D continuum, the categorisation of AOD to only include bleeds of certain bacteria seems likely to be too specific and by definition should only describe the period of time under which the tree have been declining.
Perhaps subcategories of AOD would be more suitable such as Agrilus associated AOD or Armillaria associated AOD. 
- Thresholds for decline groupings within index ranges
- Validation of decline scores - chicken and paradox
- Refined definition of remission

>>>>

- Accessability of collecting descriptors
- Suitability of collected phenotypic descriptors for describing decline status
- Concession of model interpretability to predictive capability by using a machine learning approach
- Trends of key phenotypic descriptors withing the PDI and DAI measures
- Sensitivity provided for integration with large scale omics analyses as well as long term monitoring for forest condition
- Index thresholds for category definitions (healthy, declining, severe decline etc.)
- Semi-supervised can be used if unsupervised model is unable to pull out decline severity scale
- Scalability of method for wider application
- When viewed in the 2D continuum, the categorisation of AOD to only include bleeds of certain bacteria seems likely to be too specific and by definition should only describe the period of time under which the tree have been declining.
Perhaps subcategories of AOD would be more suitable such as Agrilus associated AOD or Armillaria associated AOD. 
- Thresholds for decline groupings within index ranges
- Validation of decline scores - chicken and paradox
- Refined definition of remission
- use of unsupervised over supervised analysis
